\mytitle

### 2022-04-08 report/report.tex
Update

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{chirp}
	\caption{Left: transmitted (TX) and received (RX) sawtooth chirps and their difference frequency (IF). Right: illustration of TX chirp waveform. (Own work)}
	\label{fig:Chirp}
\end{figure}

@@

\subsection{Signal averaging}
Explain with signal averaging we can get \(\sqrt{N}\) improvement in SNR, why that's necessary to detect clouds

@@

\section{Requirements}
There are two software implementations to date, named Mark I and Mark II.
Mark I

Mark II supports real-time data acquisition (see Sec. \ref{sc:AltToDblBuf}) and saving of raw data (\acrshort{ac:adc} integers) to disk, however does not perform any processing beyond a range-Doppler plot for each \acrshort{ac:cpi}.

@@

@@

\subsection{FMCW-Doppler processing}
The software uses a third-party library, \acrshort{ac:fftw} v3\cite{FFTWv3}, for the two discrete Fourier transform steps in the FMCW-Doppler process.

@@

In \acrshort{ac:fftw}, \textit{plans} are created

>>>>

Science is often highly collaborative. Please clarify here which parts of the work reported have been done by you and which parts include the work of others.

For example, this might include provision of simulation or analysis codes which you utilised or modified, provision of experimental data to analyse, collaborations wit others in performing new measurements, if you built up things from scratch in your project or started from pre-existing setups, and others. Providing this information helps clarify the scope and focus of your project work.

\begin{itemize}
	\item Mark I code was supplied by Dr Duncan Robertson.
	\item Mark II code was developed by Dr Samiur Rahman.
	\item New code is a complete rewrite from scratch.
\end{itemize}

\clearpage
\setcounter{page}{1}

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{chirp}
	\caption{Left: transmitted (TX) and received (RX) sawtooth chirps and the intermediate frequency (\acrshort{ac:if}). Right: illustration of TX chirp waveform. (Own work)}
	\label{fig:Chirp}
\end{figure}

@@

\subsection{Signal averaging}
In this context, a \textit{frame} is a sequence of \acrshort{ac:cpi}s to be averaged together.

Explain with signal averaging we can get \(\sqrt{N}\) improvement in SNR, why that's necessary to detect clouds

@@

\section{Requirements}
\subsection{Current state of radar software}
There are two software implementations to date, named Mark I and Mark II.

Mark I

Mark II supports real-time data acquisition (see Sec. \ref{sc:AltToDblBuf}) and saving of raw data (\acrshort{ac:adc} integers) to disk, however does not perform any processing beyond a range-Doppler plot for each \acrshort{ac:cpi}. While the data acquisition is real-time, it is not continuous.

@@

\subsection{Project goals}
The main project goals are:
\paragraph{Continuous real-time processing.} Ensure no frames are dropped and the processing is real-time.

\paragraph{User interface} Combine hardware control and sensors into new code. Implement two different modes of display: operational (range and velocity resolution, etc.) and engineering (bandwidth, etc.). Add plot showing reflectivity as a function of range and time.

\paragraph{Signal averaging.} Implement averaging of power spectra and range-Doppler data to significantly improve sensitivity to clouds.

\paragraph{Doppler moments.} Display velocity spectrum for a particular range bin and calculate its moments.

\paragraph{Calibration.} Convert output from \(\si{\deci\belm}\) to \(\si{\deci\belz}\).

\paragraph{Effect of ambient temperature.} Sensors inside the radar enclosure can record the temperature. Record temperature over a long period of time and correlate to radar performance.

\paragraph{Cross-check results with a disdrometer.} Use adjacent disdrometer to record the drop-size distribution while raining. The reflectivity can then be calculated and compared to the radar output.

@@

\subsection{FMCW-Doppler processing}
The software uses a third-party library, \acrshort{ac:fftw} v3 (\cite{FFTWv3}), for the two discrete Fourier transform steps in the FMCW-Doppler process.

@@
